Safe Memory Regions for Big Data Processing

### 2016-10-18 paper/overview2.tex
Final changes.
minor changes

The \C{Region} constructor takes as a parameter a function that
constructs the root object: it creates a new region and invokes this
function, with the new region as the allocation context, to create the
root object of the region. The following code illustrates the
creation of a transferable region, whose root is an object of type
\C{A}.
% (\C{r}) of type \C{T}:
\begin{codejava} 
  Region<A> rgn = new Region<T>(() => new A())
\end{codejava} 
In the above code, \C{rgn} is called the \emph{handler} to the newly
created region, and is required to read the contents of the region, or
change its state. The class \C{Region} offers two methods: a \C{free}
method that deallocates the region (and all the objects allocated
within it), and \C{transfer} method that transfers the region to a
(possibly remote) consumer process. 
% It is an abstraction of two possible forms of
% transfer: a transfer between two processes in a shared memory setting
% or a transfer between two processes in a distributed, message-passing,
% setting. 
% The precise semantics of \C{transfer} are unimportant in the
% context of the region type system and we will not discuss them
% further. \dv{this is a bit counter-intuitive.}

@@

\paragraph{Motivating Example}
% We now illustrate how the features of \name can be used to 
Fig.~\ref{fig:motivating-eg-in-broom} shows how the motivating example
of Fig.~\ref{fig:motivating-eg} can be written in \name.  The
\C{onReceive} method receives its input message in a
\emph{transferred} region (\ie, a \emph{closed} region whose ownership
is transferred to the recipient).  Line 7 creates a new region to
store the output for time \C{t}, initializing it to contain an empty
list.  Line 9 opens the input region to process it\footnote{We omit
\C{@R} annotation in \C{open} when we don't need \C{R}.}.  Line 10
creates a stack region \C{R0}.  Thus, the temporary objects created by
the iteration in line 11, for example, will be allocated in this stack
region that lives just long enough.  We open the desired output region
in line 12, so that the new output objects created by the invocation
of \C{selector} in line 13 are allocated in the output region.
Finally, the input region is freed in line 15. The output region at
\C{map[t]} stays as along as input messages with timestamp \C{t} keep
arriving. When the timing message for \C{t} arrives, the \C{onNotify}
method transfers the \C{outRgn} at \C{map[t]} to a downstream actor.
% After the transfer, \C{SelectVertex} is no longer allowed to access
% the \C{outRgn}, facilitating its deallocation.

>>>>

The \C{Region} constructor takes as a parameter a function that
constructs the root object: it creates a new region and invokes this
function, with the new region as the allocation context, to create the
root object of the region. The following code illustrates the
creation of a transferable region, whose root is an object of type
\C{A}.
% (\C{r}) of type \C{T}:
\begin{codejava} 
  Region<A> rgn = new Region<A>(() => new A())
\end{codejava} 
In the above code, \C{rgn} is called the \emph{handler} to the newly
created region, and is required to read the contents of the region, or
change its state. The class \C{Region} offers two methods: a \C{free}
method that deallocates the region (and all the objects allocated
within it), and \C{transfer} method that transfers the region to a
(possibly remote) consumer process. 
% It is an abstraction of two possible forms of
% transfer: a transfer between two processes in a shared memory setting
% or a transfer between two processes in a distributed, message-passing,
% setting. 
% The precise semantics of \C{transfer} are unimportant in the
% context of the region type system and we will not discuss them
% further. \dv{this is a bit counter-intuitive.}

@@

\paragraph{Motivating Example}
% We now illustrate how the features of \name can be used to 
Fig.~\ref{fig:motivating-eg-in-broom} shows how the motivating example
of Fig.~\ref{fig:motivating-eg} can be written in \name.  The
\C{onReceive} method receives its input message in a
\emph{transferred} region (\ie, a \emph{closed} region whose ownership
is transferred to the recipient).  Line 7 creates a new region to
store the output for time \C{t}, initializing it to contain an empty
list.  Line 8 opens the input region to process it.
% \footnote{We omit \C{@R} annotation in \C{open} when we don't need \C{R}.}
Line 9 creates a stack region \C{R0}.  Thus, the temporary objects created by
the iteration in line 10, for example, will be allocated in this stack
region that lives just long enough.  We open the desired output region
in line 11, so that the new output objects created by the invocation
of \C{selector} in line 12 are allocated in the output region.
Finally, the input region is freed in line 14. The output region at
\C{map[t]} stays as along as input messages with timestamp \C{t} keep
arriving. When the timing message for \C{t} arrives, the \C{onNotify}
method transfers the \C{outRgn} at \C{map[t]} to a downstream actor.
% After the transfer, \C{SelectVertex} is no longer allowed to access
% the \C{outRgn}, facilitating its deallocation.
